\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
structure results and discussion section

\subsection{Results}

\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
	\end{tabular}
\caption{overall time} 
\end{table}

\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 23\% & 52\% & 23\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 17\% & 58\% & 25\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 27\% & 40\% & 29\% & 3\% \\
	E3 & 20\% & 57\% & 21\% & 2\% \\
	\end{tabular}
\caption{active time} 
\end{table}

@@

% new people still spent time configuring their proxy!

%%% SUCCESS RATE 
% TODO: impact of env on success (chi squared?.. Serge might be wrong on this) 
% TODO: impact of version on success (chi squared?.. Serge might be wrong on this)

%%% RIGHT CLAMP TIME 
% done
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

%%% RIGHT CLAMP ACTIVE TIME 
% TODO:  time to success graph with right clamped ``active time''
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:01 \\
	E2-NEW & 18/19 & 95\% & 3:22 \\
	E2-OLD & 16/19 & 84\% & 4:01 \\
	E3-NEW & 13/20 & 65\% & 12:38 \\
	E3-OLD & 10/20 & 50\% & 18:16 \\
	\end{tabular}
\caption{A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were not used to calculate the median time
to success.}
\end{table}

%\begin{figure}
%\centering
%\includegraphics{time_to_success}
%\caption{
%Time to first success, by censorship environment and interface.
%The dots show the raw completion times;
%while the boxplots show the medians and interquartile ranges.
%The ``DNF'' figures at the right
%show the number of participants who did not finish
%in the time alloted.
%}
%\label{fig:time_to_success}
%\end{figure}

\begin{table}
\centering 
	% Generated by info.R:
	\begin{tabular}{l r r r r}
	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
	\noalign{\hrule}
	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
	\end{tabular}
\caption{This Table shows what the success rate would have been
at different cutoff times.
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
\end{table}

\begin{figure} 
%\includegraphics{}
{\color {red} TODO} 
\caption{time spent on each screen}
\end{figure}

\section{Discussion} 
{\color {red} TODO: remaining issues.} \\
{\color {red} recommendations are below.} \\

@@

Despite giving 5 of the participants downloaded Tor

>>>>

\subsection{Results} 
Out of our 124 participants,  we have 116 valid data points. {\color {red} TODO} participants downloaded their own version of Tor, and {\color {red} TODO} participants did not sign the consent form. We have 58 valid participants who tested the new interface, and 58 who tested the old interface. 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3. Table~\ref{table:participant-summary} summarizes participants' success based on their interface version and environment combination.

The impact of the version on success rate is (significant,not significant). 
The impact of the environment on success rate is (significant,not significant). 
% SUCCESS
% TODO: impact of version on success (chi squared?.. Serge might be wrong on this) 
% TODO: impact of env on success (chi squared?.. Serge might be wrong on this)

Talk about why we chose to assign the max time of 40 minutes to did not finish. 
The impact of the version on time to completion is (significant,not significant). 
The impact of the environment on time to completion is (significant,not significant).
Figure~\ref{fig:time_to_success_clamped}
%%% RIGHT CLAMP TIME 
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

%TODO: FIX THIS SO THAT MEDIAN TIMES REFLECT DNF=40 minutes.
\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:01 \\
	E2-NEW & 18/19 & 95\% & 3:22 \\
	E2-OLD & 16/19 & 84\% & 4:01 \\
	E3-NEW & 13/20 & 65\% & 12:38 \\
	E3-OLD & 10/20 & 50\% & 18:16 \\
	\end{tabular}
\caption{{\color{red} TODO: FIX THIS SO THAT MEDIAN TIMES REFLECT DNF=40 minutes.}
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were not used to calculate the median time
to success.}
\label{table:participant-summary}
\end{table}

Our participants had 40 minutes. In real life, people may give up a lot sooner. 
Figure~\ref{fig:time_to_success_ecdf}. Table~\ref{table:less_time}.

\begin{table}
\centering 
	% Generated by info.R:
	\begin{tabular}{l r r r r}
	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
	\noalign{\hrule}
	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
	\end{tabular}
\caption{This Table shows what the success rate would have been
at different cutoff times.
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
\label{table:less_time}
\end{table}

\section{Discussion}

People spent a lot of time just waiting at the progress bar.

Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
The impact of the version on active time is (significant,not significant). 
The impact of the environment on active time is (significant,not significant).
%%% RIGHT CLAMP ACTIVE TIME 
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
{\color{red} MAKE THIS FOR ACTIVE TIME}
}
\label{fig:active_time_clamped}
\end{figure}

%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
	\end{tabular}
\caption{overall time} 
\label{table:overall_time}
\end{table}

%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 23\% & 52\% & 23\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 17\% & 58\% & 25\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 27\% & 40\% & 29\% & 3\% \\
	E3 & 20\% & 57\% & 21\% & 2\% \\
	\end{tabular}
\caption{active time} 
\label{table:active_time}
\end{table}

% impacts of making the proxy page ``automated'' 
New people still spent time configuring their proxy!

% impacts of making bridge page collapsed 
This is unclear. And people didn't really see our advice that we put on the page.

@@

%FAILURES
Elaborate on why people failed:  
\begin{enumerate}
\item only tried connecting directly (8/23)
\item didn't know what to do after connecting directly and default bridge (6/23)
\item Thought that they needed a proxy (6/23)
\item used the bridges auto-responder incorrectly (3/23)
\end{enumerate}

@@

Mention of people downloading their own Tor.
